Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 \MakeLowercase{b}

### 2018-10-01 ms.tex
a little more comparison with WD 1145+017.

\added{
We note that the long-term evolution of the transit depths and shape may be similar to the trends observed on WD1145+017 \citep{gary2017photometricObsWD1145p017,rappaport2018opticalActivityWD1145p017}.
WD1145+017 also changes its transit activity on $\sim$ month long timescales.
These trends in transit activity are explained by either random collisions of asteroids or variable dust emission of asteroids.
We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b could have long term behavior determined by surface features.
If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate.
Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors.
}

>>>>

\added{
We note that the long-term evolution of the transit depths and shape may be similar to the trends observed on WD1145+017 \citep{gary2017photometricObsWD1145p017,rappaport2018opticalActivityWD1145p017}.
WD1145+017 also changes its transit activity on $\sim$ month long timescales.
These trends in transit activity are explained by either random collisions of asteroids or variable dust emission of asteroids.

We suspect that sublimating asteroids around WD1145+017, the \sha\ and K2-22 b have long term behavior determined by surface features.
If alternating layers of rocky material have different composition, sublimation temperatures or albedos, they could provide a natural way to regulate the sublimation rate of the surface.
Alternatively, the chance alignment of starspots with the planet could regulate the planet disintegration \citep{kawahara2013starspots} and create periodic behaviors depending on the alignment of stellar rotation with the planet's position within its orbit.
\sha\ exhibits large stochastic variance that occasionally shuts off during quiescent intervals.
The transit activity level of WD1145+017's exhibits more complicated time dependence because there are many separate planetesimals or recently broken-up fragments that can serve as sources of dust \citep{vanderburg2015wdDisintegrating}.
}
